Choosing Color Palettes for Statistical Graphics

### 2007-01-07 trunk/vcd/paper/Color/TAS.Rnw
small fixes
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@636 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\setkeys{Gin}{width=\textwidth}
\begin{figure}[h!]
\begin{center}
<<haireye, fig=TRUE, height=5.5, width=12>>=
he <- margin.table(HairEyeColor, 1:2)
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 2)))
pushViewport(viewport(layout.pos.col=1, layout.pos.row=1))
mosaic(he, gp = shading_hsv, split_vertical = TRUE, newpage = FALSE, legend = FALSE)
popViewport()
pushViewport(viewport(layout.pos.col=2, layout.pos.row=1))
mosaic(he, gp = shading_hcl, split_vertical = TRUE, newpage = FALSE, legend = FALSE)
popViewport(2)
@
\caption{\label{fig:haireye} Extended mosaic display for haireye data.}
\end{center}
\end{figure}

@@

>>>>

\setkeys{Gin}{width=\textwidth}
\begin{figure}[h!]
\begin{center}
<<haireye, fig=TRUE, height=5.5, width=12>>=
he <- margin.table(HairEyeColor, 1:2)
grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 2)))
pushViewport(viewport(layout.pos.col=1, layout.pos.row=1))
mosaic(he, gp = shading_hsv, split_vertical = TRUE, newpage = FALSE, legend = FALSE)
popViewport()
pushViewport(viewport(layout.pos.col=2, layout.pos.row=1))
mosaic(he, gp = shading_hcl, split_vertical = TRUE, newpage = FALSE, legend = FALSE)
popViewport(2)
@
\caption{\label{fig:haireye} Extended mosaic display for hair and eye color data.}
\end{center}
\end{figure}

@@

<<barplot, eval=FALSE>>=
x <- rbind(
c(255, 255, 111),
c(255, 255,  47),
c(120,  50,   1),
c(102, 204, 102),
c( 50, 204, 204),
c(203, 153, 204),
c(102, 204, 102),
c(255,  47,  47),
c(102, 204, 102))/255

y <- c(10, 20, 25, 18, 16, 13, 21, 15, 18) - 3

par(mfrow = c(1, 2))
barplot(y, col = hex(RGB(x[,1], x[,2], x[,3])), space = 0)
## barplot(y, col = hcl(attr(as(RGB(x[,1], x[,2], x[,3]), "polarLUV"), "coords")[,"H"],
##  c = 40, l = 80), space = 0)
barplot(y, col = rainbow_hcl(7, c = 40, l = 80)[c(3, 5, 2, 4, 6, 1, 4, 7, 4)], space = 0)
@
